Automatically Proving Equivalence by Type-Safe Reflection

### 2017-03-31 paper-CICM-17/paper.tex
Needs more proofreading and if possible english check by Edwin
CICM-17 : final fixes
CICM-17 : removed comma

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}
%
\usepackage{makeidx}  % allows for indexgeneration

@@

\mainmatter              % start of the contributions
%
\title{Automatically Proving Equivalence by Type-Safe Reflection}
\subtitle{Or how to use dependent types to address some of the problems they have caused}
%
\titlerunning{xxx}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Franck Slama \and Edwin Brady}
\institute{University of St Andrews, Scotland, UK,\\
\email{fs39@st-andrews.ac.uk, ecb10@st-andrews.ac.uk}}

@@

\keywords{proof automation, equivalence, equality, proof by reflection, correct-by-construction software}
\end{abstract}
%

>>>>

% Franck Slama's and Edwin Brady's paper for CICM-2017
% That follows the LLNCS style from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}
%
\usepackage{makeidx}  % allows for indexgeneration

@@

\mainmatter              % start of the contributions
%
\title{Automatically Proving Equivalence by Type-Safe Reflection}
\subtitle{Or how to use dependent types to address some of the problems they have caused}
%
\titlerunning{xxx}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Franck Slama \and Edwin Brady}
\institute{University of St Andrews, Scotland, UK\\
\email{fs39@st-andrews.ac.uk, ecb10@st-andrews.ac.uk}}

@@

\keywords{proof automation, equivalence, equality, proof by reflection, correct-by-construction software, type-driven development}
\end{abstract}
%
